One Step Closer to Version 1.0

### 2018-03-27 GSoC/GSoC.tex
GSoC: Final Proposal
Signed-off-by: Rohit Das <rohit.das950@gmail.com>

					\begin{itemize}
					\item {Since js classes aren’t available in Qt, each component will be implemented with its own separate js file, and exported as a module to be used in circuits.}

@@

			\item[$\square$] {Components mentioned earlier will be introduced into the activity at a much later stage, since these will require a much thorough knowledge even for using in a basic circuit.}
			\end{itemize}
		\end{itemize}
\bigskip\bigskip

@@

{June 16 - June 25} & \par
\parbox{12cm}{
\begin{itemize}[noitemsep, topsep=2pt]
	\item Work on developing tutorials easy enough to be understood by children. The tutorials shall be built first so as to give an insight on how to proceed to make future components next.

	\begin{itemize}[noitemsep, topsep=2pt]
		\item Tutorials for resistors shall consist of pictures depicting what and why of a resistor, followed by how to use them, and analogies to taps being used to restrict water flow similar to resistors restricting current flow.

@@

	\end{itemize}
\end{itemize}
}\\
\hline

 & \par
 \parbox{12cm}{
	\begin{itemize}[noitemsep, topsep=2pt]
		\item[] 
		\begin{itemize}[noitemsep, topsep=2pt]
			\item For solenoids, a tutorial level will be included where magnetism will be exhibited as follows: a solenoid connected with a battery will be shown. An image of iron nails kept nearby shall be animated to move nearer the solenoid, depicting attraction. In the tutorial, a brief description of a magnet and why it attracts only certain materials.
		\end{itemize}
	\end{itemize}	 
 }\\
 \hline

@@

\section{About Me}
\label{S:1}
{I am currently in my final year at Maulana Abul Kalam Azad University of Technology (formerly WBUT), Kolkata, pursuing B. Tech. in Computer Science and Engineering. I have been contributing to the Qt version of GCompris since September 2017. Some of my contributions are:}
\begin{itemize}
\item {Removed dependency of ball direction on mouse buttons in Penalty activity:\\
\href{https://cgit.kde.org/gcompris.git/commit/?id=c94d7454c5a05364a1cbeae5b0bd1bed552ae5ed}{https://cgit.kde.org/gcompris.git/commit/?id=c94d7454c5a05364a1cbeae5b0bd1bed552ae5ed}}

\item {Progress bar corresponding to click zone only will be animated in Penalty activity:\\
 \href{https://cgit.kde.org/gcompris.git/commit/?id=e5b68f68657cf1ac25a6aa31924acfaf4a180f0b}{https://cgit.kde.org/gcompris.git/commit/?id=e5b68f68657cf1ac25a6aa31924acfaf4a180f0b}}

\item {Added easy mode in Letter-In-Word activity:\\
\href{https://cgit.kde.org/gcompris.git/commit/?id=c48f7057c27166edc6b8297bb3518a10ec2ee31b}{https://cgit.kde.org/gcompris.git/commit/?id=c48f7057c27166edc6b8297bb3518a10ec2ee31b}}

\item {Improved layout in Hangman activity:\\
\href{https://cgit.kde.org/gcompris.git/commit/?id=6a66cd44106015bd369616574d656a8dd19d15be}{https://cgit.kde.org/gcompris.git/commit/?id=6a66cd44106015bd369616574d656a8dd19d15be}}

\item {Fixed coding style issues for Ascending-Order activity:\\
\href{https://cgit.kde.org/gcompris.git/commit/?id=ade955e042ceb9774459a1181382159606a31502}{https://cgit.kde.org/gcompris.git/commit/?id=ade955e042ceb9774459a1181382159606a31502}}

\item {Added option to change case of letter to find in Letter-In-Word activity:\\
\href{https://commits.kde.org/gcompris/7c769594a5372e560904511404e2d1e156904050}{https://commits.kde.org/gcompris/7c769594a5372e560904511404e2d1e156904050}}
\end{itemize}
\bigskip
\textbf{Website: }\href{mouri11.github.io}{mouri11.github.io}\\
\textbf{Contact Info:}\\
\textbf{Email: }{Rohit Das $[$rohit.das950@gmail.com$]$}\\
\textbf{IRC Nick: } mouri11

>>>>

					\begin{itemize}
					\item {Since js classes are not available in Qt, each component will be implemented with its own separate js file, and exported as a module to be used in circuits.}

@@

			\item[$\square$] {Components mentioned earlier will be introduced into the activity at a much later stage, since these will require a much thorough knowledge even for using in a basic circuit.}
			\end{itemize}

		\item[$\blacksquare$] \textbf{Unit Testing and Documentation:}
			\begin{itemize}
			\item[$\square$] {The framework to automate unit testing will be developed in GSoC 18 most probably, so unit testing will be handled by that.}

			\item[$\square$] {Comments mentioning the function of various methods and variables will be put in the code as necessary.}
			\end{itemize}
		\end{itemize}
\bigskip\bigskip

@@

{June 16 - June 25} & \par
\parbox{12cm}{
\begin{itemize}[noitemsep, topsep=2pt]
	\item Work on developing tutorials easy enough to be understood by children. The tutorials shall be built first so as to give an insight on how to proceed to make future components next.
	\begin{itemize}[noitemsep, topsep=2pt]
		\item Tutorials for resistors shall consist of pictures depicting what and why of a resistor, followed by how to use them, and analogies to taps being used to restrict water flow similar to resistors restricting current flow.
	\end{itemize}
\end{itemize}
}\\
\hline

  & \par
\parbox{12cm}{
\begin{itemize}[noitemsep, topsep=2pt]
	\item[] 
	\begin{itemize}[noitemsep, topsep=2pt]

@@

		\item For solenoids, a tutorial level will be included where magnetism will be exhibited as follows: a solenoid connected with a battery will be shown. An image of iron nails kept nearby shall be animated to move nearer the solenoid, depicting attraction. In the tutorial, a brief description of a magnet and why it attracts only certain materials.
		\end{itemize}
	\end{itemize}	 
 }\\
 \hline

@@

\section{About Me}
\label{S:1}
{I am currently in my final year at Maulana Abul Kalam Azad University of Technology (formerly WBUT), Kolkata, pursuing B. Tech. in Computer Science and Engineering. I have been contributing to the Qt version of GCompris since September 2017. Some of my contributions are:}
\begin{itemize}
\item {Removed dependency of ball direction on mouse buttons in \textit{Penalty} activity:\\
\href{https://cgit.kde.org/gcompris.git/commit/?id=c94d7454c5a05364a1cbeae5b0bd1bed552ae5ed}{https://cgit.kde.org/gcompris.git/commit/?id=c94d7454c5a05364a1cbeae5b0bd1bed552ae5ed}}

\item {Progress bar corresponding to click zone only will be animated in \textit{Penalty} activity:\\
 \href{https://cgit.kde.org/gcompris.git/commit/?id=e5b68f68657cf1ac25a6aa31924acfaf4a180f0b}{https://cgit.kde.org/gcompris.git/commit/?id=e5b68f68657cf1ac25a6aa31924acfaf4a180f0b}}

\item {Added easy mode in \textit{Letter-In-Word} activity:\\
\href{https://cgit.kde.org/gcompris.git/commit/?id=c48f7057c27166edc6b8297bb3518a10ec2ee31b}{https://cgit.kde.org/gcompris.git/commit/?id=c48f7057c27166edc6b8297bb3518a10ec2ee31b}}

\item {Improved layout in \textit{Hangman} activity:\\
\href{https://cgit.kde.org/gcompris.git/commit/?id=6a66cd44106015bd369616574d656a8dd19d15be}{https://cgit.kde.org/gcompris.git/commit/?id=6a66cd44106015bd369616574d656a8dd19d15be}}

\item {Fixed coding style issues for \textit{Ascending-Order} activity:\\
\href{https://cgit.kde.org/gcompris.git/commit/?id=ade955e042ceb9774459a1181382159606a31502}{https://cgit.kde.org/gcompris.git/commit/?id=ade955e042ceb9774459a1181382159606a31502}}

\item {Added option to change case of letter to find in \textit{Letter-In-Word} activity:\\
\href{https://commits.kde.org/gcompris/7c769594a5372e560904511404e2d1e156904050}{https://commits.kde.org/gcompris/7c769594a5372e560904511404e2d1e156904050}}
\end{itemize}
\bigskip
\textbf{Website: }\href{https://mouri11.github.io}{https://mouri11.github.io}\\
\textbf{Contact Info:}\\
\textbf{Email: }{Rohit Das $[$rohit.das950@gmail.com$]$}\\
\textbf{IRC Nick: } mouri11
